---
title: "Water Chem 2"
author: "Emily Huff and James Wood"
date: "6/26/2021"
output: html_document
---


#loading stuff
```{r}
waterchem2 <- read.csv("Water Chem.csv")

library(ggplot2)
library(cowplot)

WeCr <- subset(waterchem2, Site== "WeCr03"|Site=="WeCr07"|Site== "WeCr09"|Site== "WeCr11"|Site=="LrCr"|Site== "WdCr"|Site=="PrCr"|Site== "FdCr"|Site=="OhRv01"|Site== "OhRv02")

NfSh <- subset(waterchem2, Site== "NoFr03"|Site=="NoFr02"|Site== "NoFr01"|Site=="WrCr"|Site=="ShCr02"|Site== "ShCr05"|Site=="ShCr06")

BfCr <- subset(waterchem2, Site=="BfCr02"|Site== "CmCr")

AMDs <- subset(waterchem2, Site== "ChCr01"|Site=="NrCr"|Site== "CsCr")

WeCr03 <- subset(waterchem2, Site=="WeCr03")
WeCr07 <- subset(waterchem2, Site=="WeCr07")
WeCr09 <- subset(waterchem2, Site=="WeCr09")
WeCr11 <- subset(waterchem2, Site=="WeCr11")
LrCr <- subset(waterchem2, Site=="LrCr")
WdCr <- subset(waterchem2, Site=="WdCr")
FdCr <- subset(waterchem2, Site=="FdCr")
PrCr <- subset(waterchem2, Site=="PrCr")
WrCr <- subset(waterchem2, Site=="WrCr")
NoFr03 <- subset(waterchem2, Site=="NoFr03")
NoFr02 <- subset(waterchem2, Site=="NoFr02")
NoFr01 <- subset(waterchem2, Site=="NoFr01")
ShCr02 <- subset(waterchem2, Site=="ShCr02")
ShCr05 <- subset(waterchem2, Site=="ShCr05")
ShCr06 <- subset(waterchem2, Site=="ShCr06")
BfCr02 <- subset(waterchem2, Site=="BfCr02")
CmCr <- subset(waterchem2, Site=="CmCr")
OhRv01 <- subset(waterchem2, Site=="OhRv01")
OhRv02 <- subset(waterchem2, Site=="OhRv02")
ChCr01 <- subset(waterchem2, Site=="ChCr01")
NrCr <- subset(waterchem2, Site=="NrCr")
CsCr <- subset(waterchem2, Site=="CsCr")
```

#Plots for slopes by site 
## All site data Chloride vs Conductivity slope and R2 values
```{r}
summary(lm.WeCr03<-lm(WeCr03$Conductivity~WeCr03$Chloride))
plot(WeCr03$Conductivity~WeCr03$Chloride)
abline(lm.WeCr03)
summary(lm.WeCr07<-lm(WeCr07$Conductivity~WeCr07$Chloride))
plot(WeCr07$Conductivity~WeCr07$Chloride)
abline(lm.WeCr07)    
summary(lm.WeCr09<-lm(WeCr09$Conductivity~WeCr09$Chloride))
plot(WeCr09$Conductivity~WeCr09$Chloride)
abline(lm.WeCr09) 
summary(lm.WeCr11<-lm(WeCr11$Conductivity~WeCr11$Chloride))
plot(WeCr11$Conductivity~WeCr11$Chloride)
abline(lm.WeCr11)  
summary(lm.LrCr<-lm(LrCr$Conductivity~LrCr$Chloride))
plot(LrCr$Conductivity~LrCr$Chloride)
abline(lm.LrCr)  
summary(lm.WdCr<-lm(WdCr$Conductivity~WdCr$Chloride))
plot(WdCr$Conductivity~WdCr$Chloride)
abline(lm.WdCr)
summary(lm.FdCr<-lm(FdCr$Conductivity~FdCr$Chloride))
plot(FdCr$Conductivity~FdCr$Chloride)
abline(lm.FdCr)
summary(lm.PrCr<-lm(PrCr$Conductivity~PrCr$Chloride))
plot(PrCr$Conductivity~PrCr$Chloride)
abline(lm.PrCr)
summary(lm.WrCr<-lm(WrCr$Conductivity~WrCr$Chloride))
plot(WrCr$Conductivity~WrCr$Chloride)
abline(lm.WrCr)
summary(lm.NoFr03<-lm(NoFr03$Conductivity~NoFr03$Chloride))
plot(NoFr03$Conductivity~NoFr03$Chloride)
abline(lm.NoFr03) 
summary(lm.NoFr02<-lm(NoFr02$Conductivity~NoFr02$Chloride))
plot(NoFr02$Conductivity~NoFr02$Chloride)
abline(lm.NoFr02) 
summary(lm.NoFr01<-lm(NoFr01$Conductivity~NoFr01$Chloride))
plot(NoFr01$Conductivity~NoFr01$Chloride)
abline(lm.NoFr01)
summary(lm.ShCr02<-lm(ShCr02$Conductivity~ShCr02$Chloride))
plot(ShCr02$Conductivity~ShCr02$Chloride)
abline(lm.ShCr02)
summary(lm.ShCr05<-lm(ShCr05$Conductivity~ShCr05$Chloride))
plot(ShCr05$Conductivity~ShCr05$Chloride)
abline(lm.ShCr05)
summary(lm.ShCr06<-lm(ShCr06$Conductivity~ShCr06$Chloride))
plot(ShCr06$Conductivity~ShCr06$Chloride)
abline(lm.ShCr06)
summary(lm.BfCr02 <-lm(BfCr02 $Conductivity~BfCr02 $Chloride))
plot(BfCr02 $Conductivity~BfCr02 $Chloride)
abline(lm.BfCr02 )
summary(lm.OhRv02<-lm(OhRv02$Conductivity~OhRv02$Chloride))
plot(OhRv02$Conductivity~OhRv02$Chloride)
abline(lm.OhRv02)
summary(lm.ChCr01<-lm(ChCr01$Conductivity~ChCr01$Chloride))
plot(ChCr01$Conductivity~ChCr01$Chloride)
abline(lm.ChCr01)
summary(lm.NrCr <-lm(NrCr $Conductivity~NrCr $Chloride))
plot(NrCr $Conductivity~NrCr $Chloride)
abline(lm.NrCr )
summary(lm.CsCr <-lm(CsCr $Conductivity~CsCr $Chloride))
plot(CsCr $Conductivity~CsCr $Chloride)
abline(lm.CsCr )
summary(lm.OhRv01 <-lm(OhRv01 $Conductivity~OhRv01 $Chloride))
plot(OhRv01 $Conductivity~OhRv01 $Chloride)
abline(lm.OhRv01 )
summary(lm.CmCr <-lm(CmCr $Conductivity~CmCr $Chloride))
plot(CmCr $Conductivity~CmCr $Chloride)
abline(lm.CmCr )
```




#Plots for slopes
###Winter 2021
```{r}
winter2021 <- read.csv("Winter 2021.csv")

WeCr03W21 <- subset(winter2021, Site=="WeCr03")
WeCr07W21 <- subset(winter2021, Site=="WeCr07")
WeCr09W21 <- subset(winter2021, Site=="WeCr09")
LrCrW21 <- subset(winter2021, Site=="LrCr")
WdCrW21 <- subset(winter2021, Site=="WdCr")
FdCrW21 <- subset(winter2021, Site=="FdCr")
PrCrW21 <- subset(winter2021, Site=="PrCr")
WrCrW21 <- subset(winter2021, Site=="WrCr")
NoFr03W21 <- subset(winter2021, Site=="NoFr03")
NoFr02W21 <- subset(winter2021, Site=="NoFr02")
NoFr01W21 <- subset(winter2021, Site=="NoFr01")
ShCr02W21 <- subset(winter2021, Site=="ShCr02")
ShCr05W21 <- subset(winter2021, Site=="ShCr05")
ShCr06W21 <- subset(winter2021, Site=="ShCr06")
BfCr02W21 <- subset(winter2021, Site=="BfCr02")
CmCrW21 <- subset(winter2021, Site=="CmCr")
OhRv01W21 <- subset(winter2021, Site=="OhRv01")
OhRv02W21 <- subset(winter2021, Site=="OhRv02")
ChCr01W21 <- subset(winter2021, Site=="ChCr01")
NrCrW21 <- subset(winter2021, Site=="NrCr")
CsCrW21 <- subset(winter2021, Site=="CsCr")

plot(WeCr03W21$Conductivity~WeCr03W21$Chloride)
abline(lm(WeCr03W21$Conductivity~WeCr03W21$Chloride))
summary(lm(WeCr03W21$Conductivity~WeCr03W21$Chloride))

plot(WeCr07W21$Conductivity~WeCr07W21$Chloride)
abline(lm(WeCr07W21$Conductivity~WeCr07W21$Chloride))
summary(lm(WeCr07W21$Conductivity~WeCr07W21$Chloride))

plot(WeCr09W21$Conductivity~WeCr09W21$Chloride)
abline(lm(WeCr09W21$Conductivity~WeCr09W21$Chloride))
summary(lm(WeCr09W21$Conductivity~WeCr09W21$Chloride))

plot(LrCrW21$Conductivity~LrCrW21$Chloride)
abline(lm(LrCrW21$Conductivity~LrCrW21$Chloride))
summary(lm(LrCrW21$Conductivity~LrCrW21$Chloride))

plot(WdCrW21$Conductivity~WdCrW21$Chloride)
abline(lm(WdCrW21$Conductivity~WdCrW21$Chloride))
summary(lm(WdCrW21$Conductivity~WdCrW21$Chloride))

plot(FdCrW21$Conductivity~FdCrW21$Chloride)
abline(lm(FdCrW21$Conductivity~FdCrW21$Chloride))
summary(lm(FdCrW21$Conductivity~FdCrW21$Chloride))

plot(PrCrW21$Conductivity~PrCrW21$Chloride)
abline(lm(PrCrW21$Conductivity~PrCrW21$Chloride))
summary(lm(PrCrW21$Conductivity~PrCrW21$Chloride))

plot(WrCrW21$Conductivity~WrCrW21$Chloride)
abline(lm(WrCrW21$Conductivity~WrCrW21$Chloride))
summary(lm(WrCrW21$Conductivity~WrCrW21$Chloride))

plot(NoFr03W21$Conductivity~NoFr03W21$Chloride)
abline(lm(NoFr03W21$Conductivity~NoFr03W21$Chloride))
summary(lm(NoFr03W21$Conductivity~NoFr03W21$Chloride))

plot(NoFr02W21$Conductivity~NoFr02W21$Chloride)
abline(lm(NoFr02W21$Conductivity~NoFr02W21$Chloride))
summary(lm(NoFr02W21$Conductivity~NoFr02W21$Chloride))

plot(NoFr01W21$Conductivity~NoFr01W21$Chloride)
abline(lm(NoFr01W21$Conductivity~NoFr01W21$Chloride))
summary(lm(NoFr01W21$Conductivity~NoFr01W21$Chloride))

plot(ShCr02W21$Conductivity~ShCr02W21$Chloride)
abline(lm(ShCr02W21$Conductivity~ShCr02W21$Chloride))
summary(lm(ShCr02W21$Conductivity~ShCr02W21$Chloride))

plot(ShCr05W21$Conductivity~ShCr05W21$Chloride)
abline(lm(ShCr05W21$Conductivity~ShCr05W21$Chloride))
summary(lm(ShCr05W21$Conductivity~ShCr05W21$Chloride))

plot(ShCr06W21$Conductivity~ShCr06W21$Chloride)
abline(lm(ShCr06W21$Conductivity~ShCr06W21$Chloride))
summary(lm(ShCr06W21$Conductivity~ShCr06W21$Chloride))

plot(BfCr02W21$Conductivity~BfCr02W21$Chloride)
abline(lm(BfCr02W21$Conductivity~BfCr02W21$Chloride))
summary(lm(BfCr02W21$Conductivity~BfCr02W21$Chloride))

plot(CmCrW21$Conductivity~CmCrW21$Chloride)
abline(lm(CmCrW21$Conductivity~CmCrW21$Chloride))
summary(lm(CmCrW21$Conductivity~CmCrW21$Chloride))

plot(OhRv01W21$Conductivity~OhRv01W21$Chloride)
abline(lm(OhRv01W21$Conductivity~OhRv01W21$Chloride))
summary(lm(OhRv01W21$Conductivity~OhRv01W21$Chloride))

plot(OhRv02W21$Conductivity~OhRv02W21$Chloride)
abline(lm(OhRv02W21$Conductivity~OhRv02W21$Chloride))
summary(lm(OhRv02W21$Conductivity~OhRv02W21$Chloride))

plot(ChCr01W21$Conductivity~ChCr01W21$Chloride)
abline(lm(ChCr01W21$Conductivity~ChCr01W21$Chloride))
summary(lm(ChCr01W21$Conductivity~ChCr01W21$Chloride))

plot(NrCrW21$Conductivity~NrCrW21$Chloride)
abline(lm(NrCrW21$Conductivity~NrCrW21$Chloride))
summary(lm(NrCrW21$Conductivity~NrCrW21$Chloride))

plot(CsCrW21$Conductivity~CsCrW21$Chloride)
abline(lm(CsCrW21$Conductivity~CsCrW21$Chloride))
summary(lm(CsCrW21$Conductivity~CsCrW21$Chloride))
```


###Winter 2020
```{r}
winter2020 <- read.csv("Winter 2020.csv")

WeCr03W20 <- subset(winter2020, Site=="WeCr03")
WeCr07W20 <- subset(winter2020, Site=="WeCr07")
WeCr09W20 <- subset(winter2020, Site=="WeCr09")
LrCrW20 <- subset(winter2020, Site=="LrCr")
WdCrW20 <- subset(winter2020, Site=="WdCr")
FdCrW20 <- subset(winter2020, Site=="FdCr")
PrCrW20 <- subset(winter2020, Site=="PrCr")
WrCrW20 <- subset(winter2020, Site=="WrCr")
NoFr03W20 <- subset(winter2020, Site=="NoFr03")
NoFr02W20 <- subset(winter2020, Site=="NoFr02")
NoFr01W20 <- subset(winter2020, Site=="NoFr01")
ShCr02W20 <- subset(winter2020, Site=="ShCr02")
ShCr05W20 <- subset(winter2020, Site=="ShCr05")
ShCr06W20 <- subset(winter2020, Site=="ShCr06")
BfCr02W20 <- subset(winter2020, Site=="BfCr02")
CmCrW20 <- subset(winter2020, Site=="CmCr")
OhRv01W20 <- subset(winter2020, Site=="OhRv01")
OhRv02W20 <- subset(winter2020, Site=="OhRv02")
ChCr01W20 <- subset(winter2020, Site=="ChCr01")
NrCrW20 <- subset(winter2020, Site=="NrCr")
CsCrW20 <- subset(winter2020, Site=="CsCr")

plot(WeCr03W20$Conductivity~WeCr03W20$Chloride)
abline(lm(WeCr03W20$Conductivity~WeCr03W20$Chloride))
summary(lm(WeCr03W20$Conductivity~WeCr03W20$Chloride))

plot(WeCr07W20$Conductivity~WeCr07W20$Chloride)
abline(lm(WeCr07W20$Conductivity~WeCr07W20$Chloride))
summary(lm(WeCr07W20$Conductivity~WeCr07W20$Chloride))

plot(WeCr09W20$Conductivity~WeCr09W20$Chloride)
abline(lm(WeCr09W20$Conductivity~WeCr09W20$Chloride))
summary(lm(WeCr09W20$Conductivity~WeCr09W20$Chloride))

plot(LrCrW20$Conductivity~LrCrW20$Chloride)
abline(lm(LrCrW20$Conductivity~LrCrW20$Chloride))
summary(lm(LrCrW20$Conductivity~LrCrW20$Chloride))

plot(WdCrW20$Conductivity~WdCrW20$Chloride)
abline(lm(WdCrW20$Conductivity~WdCrW20$Chloride))
summary(lm(WdCrW20$Conductivity~WdCrW20$Chloride))

plot(FdCrW20$Conductivity~FdCrW20$Chloride)
abline(lm(FdCrW20$Conductivity~FdCrW20$Chloride))
summary(lm(FdCrW20$Conductivity~FdCrW20$Chloride))

plot(PrCrW20$Conductivity~PrCrW20$Chloride)
abline(lm(PrCrW20$Conductivity~PrCrW20$Chloride))
summary(lm(PrCrW20$Conductivity~PrCrW20$Chloride))

plot(WrCrW20$Conductivity~WrCrW20$Chloride)
abline(lm(WrCrW20$Conductivity~WrCrW20$Chloride))
summary(lm(WrCrW20$Conductivity~WrCrW20$Chloride))

plot(NoFr03W20$Conductivity~NoFr03W20$Chloride)
abline(lm(NoFr03W20$Conductivity~NoFr03W20$Chloride))
summary(lm(NoFr03W20$Conductivity~NoFr03W20$Chloride))

plot(NoFr02W20$Conductivity~NoFr02W20$Chloride)
abline(lm(NoFr02W20$Conductivity~NoFr02W20$Chloride))
summary(lm(NoFr02W20$Conductivity~NoFr02W20$Chloride))

plot(NoFr01W20$Conductivity~NoFr01W20$Chloride)
abline(lm(NoFr01W20$Conductivity~NoFr01W20$Chloride))
summary(lm(NoFr01W20$Conductivity~NoFr01W20$Chloride))

plot(ShCr02W20$Conductivity~ShCr02W20$Chloride)
abline(lm(ShCr02W20$Conductivity~ShCr02W20$Chloride))
summary(lm(ShCr02W20$Conductivity~ShCr02W20$Chloride))

plot(ShCr05W20$Conductivity~ShCr05W20$Chloride)
abline(lm(ShCr05W20$Conductivity~ShCr05W20$Chloride))
summary(lm(ShCr05W20$Conductivity~ShCr05W20$Chloride))

plot(ShCr06W20$Conductivity~ShCr06W20$Chloride)
abline(lm(ShCr06W20$Conductivity~ShCr06W20$Chloride))
summary(lm(ShCr06W20$Conductivity~ShCr06W20$Chloride))

plot(BfCr02W20$Conductivity~BfCr02W20$Chloride)
abline(lm(BfCr02W20$Conductivity~BfCr02W20$Chloride))
summary(lm(BfCr02W20$Conductivity~BfCr02W20$Chloride))

plot(CmCrW20$Conductivity~CmCrW20$Chloride)
abline(lm(CmCrW20$Conductivity~CmCrW20$Chloride))
summary(lm(CmCrW20$Conductivity~CmCrW20$Chloride))

plot(OhRv01W20$Conductivity~OhRv01W20$Chloride)
abline(lm(OhRv01W20$Conductivity~OhRv01W20$Chloride))
summary(lm(OhRv01W20$Conductivity~OhRv01W20$Chloride))

plot(OhRv02W20$Conductivity~OhRv02W20$Chloride)
abline(lm(OhRv02W20$Conductivity~OhRv02W20$Chloride))
summary(lm(OhRv02W20$Conductivity~OhRv02W20$Chloride))

plot(ChCr01W20$Conductivity~ChCr01W20$Chloride)
abline(lm(ChCr01W20$Conductivity~ChCr01W20$Chloride))
summary(lm(ChCr01W20$Conductivity~ChCr01W20$Chloride))

plot(NrCrW20$Conductivity~NrCrW20$Chloride)
abline(lm(NrCrW20$Conductivity~NrCrW20$Chloride))
summary(lm(NrCrW20$Conductivity~NrCrW20$Chloride))

plot(CsCrW20$Conductivity~CsCrW20$Chloride)
abline(lm(CsCrW20$Conductivity~CsCrW20$Chloride))
summary(lm(CsCrW20$Conductivity~CsCrW20$Chloride))
```

###Summer 2020
```{r}
summer2020 <- read.csv("Summer 2020.csv")

WeCr03S20 <- subset(summer2020, Site=="WeCr03")
WeCr07S20 <- subset(summer2020, Site=="WeCr07")
WeCr09S20 <- subset(summer2020, Site=="WeCr09")
LrCrS20 <- subset(summer2020, Site=="LrCr")
WdCrS20 <- subset(summer2020, Site=="WdCr")
FdCrS20 <- subset(summer2020, Site=="FdCr")
PrCrS20 <- subset(summer2020, Site=="PrCr")
WrCrS20 <- subset(summer2020, Site=="WrCr")
NoFr03S20 <- subset(summer2020, Site=="NoFr03")
NoFr02S20 <- subset(summer2020, Site=="NoFr02")
NoFr01S20 <- subset(summer2020, Site=="NoFr01")
ShCr02S20 <- subset(summer2020, Site=="ShCr02")
ShCr05S20 <- subset(summer2020, Site=="ShCr05")
ShCr06S20 <- subset(summer2020, Site=="ShCr06")
BfCr02S20 <- subset(summer2020, Site=="BfCr02")
CmCrS20 <- subset(summer2020, Site=="CmCr")
OhRv01S20 <- subset(summer2020, Site=="OhRv01")
OhRv02S20 <- subset(summer2020, Site=="OhRv02")
ChCr01S20 <- subset(summer2020, Site=="ChCr01")
NrCrS20 <- subset(summer2020, Site=="NrCr")
CsCrS20 <- subset(summer2020, Site=="CsCr")

plot(WeCr03S20$Conductivity~WeCr03S20$Chloride)
abline(lm(WeCr03S20$Conductivity~WeCr03S20$Chloride))
summary(lm(WeCr03S20$Conductivity~WeCr03S20$Chloride))

plot(WeCr07S20$Conductivity~WeCr07S20$Chloride)
abline(lm(WeCr07S20$Conductivity~WeCr07S20$Chloride))
summary(lm(WeCr07S20$Conductivity~WeCr07S20$Chloride))

plot(WeCr09S20$Conductivity~WeCr09S20$Chloride)
abline(lm(WeCr09S20$Conductivity~WeCr09S20$Chloride))
summary(lm(WeCr09S20$Conductivity~WeCr09S20$Chloride))

plot(LrCrS20$Conductivity~LrCrS20$Chloride)
abline(lm(LrCrS20$Conductivity~LrCrS20$Chloride))
summary(lm(LrCrS20$Conductivity~LrCrS20$Chloride))

plot(WdCrS20$Conductivity~WdCrS20$Chloride)
abline(lm(WdCrS20$Conductivity~WdCrS20$Chloride))
summary(lm(WdCrS20$Conductivity~WdCrS20$Chloride))

plot(FdCrS20$Conductivity~FdCrS20$Chloride)
abline(lm(FdCrS20$Conductivity~FdCrS20$Chloride))
summary(lm(FdCrS20$Conductivity~FdCrS20$Chloride))

plot(PrCrS20$Conductivity~PrCrS20$Chloride)
abline(lm(PrCrS20$Conductivity~PrCrS20$Chloride))
summary(lm(PrCrS20$Conductivity~PrCrS20$Chloride))

plot(WrCrS20$Conductivity~WrCrS20$Chloride)
abline(lm(WrCrS20$Conductivity~WrCrS20$Chloride))
summary(lm(WrCrS20$Conductivity~WrCrS20$Chloride))

plot(NoFr03S20$Conductivity~NoFr03S20$Chloride)
abline(lm(NoFr03S20$Conductivity~NoFr03S20$Chloride))
summary(lm(NoFr03S20$Conductivity~NoFr03S20$Chloride))

plot(NoFr02S20$Conductivity~NoFr02S20$Chloride)
abline(lm(NoFr02S20$Conductivity~NoFr02S20$Chloride))
summary(lm(NoFr02S20$Conductivity~NoFr02S20$Chloride))

plot(NoFr01S20$Conductivity~NoFr01S20$Chloride)
abline(lm(NoFr01S20$Conductivity~NoFr01S20$Chloride))
summary(lm(NoFr01S20$Conductivity~NoFr01S20$Chloride))

plot(ShCr02S20$Conductivity~ShCr02S20$Chloride)
abline(lm(ShCr02S20$Conductivity~ShCr02S20$Chloride))
summary(lm(ShCr02S20$Conductivity~ShCr02S20$Chloride))

plot(ShCr05S20$Conductivity~ShCr05S20$Chloride)
abline(lm(ShCr05S20$Conductivity~ShCr05S20$Chloride))
summary(lm(ShCr05S20$Conductivity~ShCr05S20$Chloride))

plot(ShCr06S20$Conductivity~ShCr06S20$Chloride)
abline(lm(ShCr06S20$Conductivity~ShCr06S20$Chloride))
summary(lm(ShCr06S20$Conductivity~ShCr06S20$Chloride))

plot(BfCr02S20$Conductivity~BfCr02S20$Chloride)
abline(lm(BfCr02S20$Conductivity~BfCr02S20$Chloride))
summary(lm(BfCr02S20$Conductivity~BfCr02S20$Chloride))

plot(CmCrS20$Conductivity~CmCrS20$Chloride)
abline(lm(CmCrS20$Conductivity~CmCrS20$Chloride))
summary(lm(CmCrS20$Conductivity~CmCrS20$Chloride))

plot(OhRv01S20$Conductivity~OhRv01S20$Chloride)
abline(lm(OhRv01S20$Conductivity~OhRv01S20$Chloride))
summary(lm(OhRv01S20$Conductivity~OhRv01S20$Chloride))

plot(OhRv02S20$Conductivity~OhRv02S20$Chloride)
abline(lm(OhRv02S20$Conductivity~OhRv02S20$Chloride))
summary(lm(OhRv02S20$Conductivity~OhRv02S20$Chloride))

plot(ChCr01S20$Conductivity~ChCr01S20$Chloride)
abline(lm(ChCr01S20$Conductivity~ChCr01S20$Chloride))
summary(lm(ChCr01S20$Conductivity~ChCr01S20$Chloride))

plot(NrCrS20$Conductivity~NrCrS20$Chloride)
abline(lm(NrCrS20$Conductivity~NrCrS20$Chloride))
summary(lm(NrCrS20$Conductivity~NrCrS20$Chloride))

plot(CsCrS20$Conductivity~CsCrS20$Chloride)
abline(lm(CsCrS20$Conductivity~CsCrS20$Chloride))
summary(lm(CsCrS20$Conductivity~CsCrS20$Chloride))
```

###Summer 2019
```{r}
summer2019 <- read.csv("Summer 2019.csv")

WeCr03S19 <- subset(summer2019, Site=="WeCr03")
WeCr07S19 <- subset(summer2019, Site=="WeCr07")
WeCr09S19 <- subset(summer2019, Site=="WeCr09")
LrCrS19 <- subset(summer2019, Site=="LrCr")
WdCrS19 <- subset(summer2019, Site=="WdCr")
FdCrS19 <- subset(summer2019, Site=="FdCr")
PrCrS19 <- subset(summer2019, Site=="PrCr")
WrCrS19 <- subset(summer2019, Site=="WrCr")
NoFr03S19 <- subset(summer2019, Site=="NoFr03")
NoFr02S19 <- subset(summer2019, Site=="NoFr02")
NoFr01S19 <- subset(summer2019, Site=="NoFr01")
ShCr02S19 <- subset(summer2019, Site=="ShCr02")
ShCr05S19 <- subset(summer2019, Site=="ShCr05")
ShCr06S19 <- subset(summer2019, Site=="ShCr06")
BfCr02S19 <- subset(summer2019, Site=="BfCr02")
CmCrS19 <- subset(summer2019, Site=="CmCr")
OhRv01S19 <- subset(summer2019, Site=="OhRv01")
OhRv02S19 <- subset(summer2019, Site=="OhRv02")
ChCr01S19 <- subset(summer2019, Site=="ChCr01")
NrCrS19 <- subset(summer2019, Site=="NrCr")
CsCrS19 <- subset(summer2019, Site=="CsCr")

plot(WeCr03S19$Conductivity~WeCr03S19$Chloride)
abline(lm(WeCr03S19$Conductivity~WeCr03S19$Chloride))
summary(lm(WeCr03S19$Conductivity~WeCr03S19$Chloride))

plot(WeCr07S19$Conductivity~WeCr07S19$Chloride)
abline(lm(WeCr07S19$Conductivity~WeCr07S19$Chloride))
summary(lm(WeCr07S19$Conductivity~WeCr07S19$Chloride))

plot(WeCr09S19$Conductivity~WeCr09S19$Chloride)
abline(lm(WeCr09S19$Conductivity~WeCr09S19$Chloride))
summary(lm(WeCr09S19$Conductivity~WeCr09S19$Chloride))

plot(LrCrS19$Conductivity~LrCrS19$Chloride)
abline(lm(LrCrS19$Conductivity~LrCrS19$Chloride))
summary(lm(LrCrS19$Conductivity~LrCrS19$Chloride))

plot(WdCrS19$Conductivity~WdCrS19$Chloride)
abline(lm(WdCrS19$Conductivity~WdCrS19$Chloride))
summary(lm(WdCrS19$Conductivity~WdCrS19$Chloride))

plot(FdCrS19$Conductivity~FdCrS19$Chloride)
abline(lm(FdCrS19$Conductivity~FdCrS19$Chloride))
summary(lm(FdCrS19$Conductivity~FdCrS19$Chloride))

plot(PrCrS19$Conductivity~PrCrS19$Chloride)
abline(lm(PrCrS19$Conductivity~PrCrS19$Chloride))
summary(lm(PrCrS19$Conductivity~PrCrS19$Chloride))

plot(WrCrS19$Conductivity~WrCrS19$Chloride)
abline(lm(WrCrS19$Conductivity~WrCrS19$Chloride))
summary(lm(WrCrS19$Conductivity~WrCrS19$Chloride))

plot(NoFr03S19$Conductivity~NoFr03S19$Chloride)
abline(lm(NoFr03S19$Conductivity~NoFr03S19$Chloride))
summary(lm(NoFr03S19$Conductivity~NoFr03S19$Chloride))

plot(NoFr02S19$Conductivity~NoFr02S19$Chloride)
abline(lm(NoFr02S19$Conductivity~NoFr02S19$Chloride))
summary(lm(NoFr02S19$Conductivity~NoFr02S19$Chloride))

plot(NoFr01S19$Conductivity~NoFr01S19$Chloride)
abline(lm(NoFr01S19$Conductivity~NoFr01S19$Chloride))
summary(lm(NoFr01S19$Conductivity~NoFr01S19$Chloride))

plot(ShCr02S19$Conductivity~ShCr02S19$Chloride)
abline(lm(ShCr02S19$Conductivity~ShCr02S19$Chloride))
summary(lm(ShCr02S19$Conductivity~ShCr02S19$Chloride))

plot(ShCr05S19$Conductivity~ShCr05S19$Chloride)
abline(lm(ShCr05S19$Conductivity~ShCr05S19$Chloride))
summary(lm(ShCr05S19$Conductivity~ShCr05S19$Chloride))

plot(ShCr06S19$Conductivity~ShCr06S19$Chloride)
abline(lm(ShCr06S19$Conductivity~ShCr06S19$Chloride))
summary(lm(ShCr06S19$Conductivity~ShCr06S19$Chloride))

plot(BfCr02S19$Conductivity~BfCr02S19$Chloride)
abline(lm(BfCr02S19$Conductivity~BfCr02S19$Chloride))
summary(lm(BfCr02S19$Conductivity~BfCr02S19$Chloride))

plot(CmCrS19$Conductivity~CmCrS19$Chloride)
abline(lm(CmCrS19$Conductivity~CmCrS19$Chloride))
summary(lm(CmCrS19$Conductivity~CmCrS19$Chloride))

plot(OhRv01S19$Conductivity~OhRv01S19$Chloride)
abline(lm(OhRv01S19$Conductivity~OhRv01S19$Chloride))
summary(lm(OhRv01S19$Conductivity~OhRv01S19$Chloride))

plot(OhRv02S19$Conductivity~OhRv02S19$Chloride)
abline(lm(OhRv02S19$Conductivity~OhRv02S19$Chloride))
summary(lm(OhRv02S19$Conductivity~OhRv02S19$Chloride))

plot(ChCr01S19$Conductivity~ChCr01S19$Chloride)
abline(lm(ChCr01S19$Conductivity~ChCr01S19$Chloride))
summary(lm(ChCr01S19$Conductivity~ChCr01S19$Chloride))

plot(NrCrS19$Conductivity~NrCrS19$Chloride)
abline(lm(NrCrS19$Conductivity~NrCrS19$Chloride))
summary(lm(NrCrS19$Conductivity~NrCrS19$Chloride))

plot(CsCrS19$Conductivity~CsCrS19$Chloride)
abline(lm(CsCrS19$Conductivity~CsCrS19$Chloride))
summary(lm(CsCrS19$Conductivity~CsCrS19$Chloride))
```



#Winter Stream Chloride
```{r}

BfCr022020 <-c(9.88, 11, 10.73, 6.69, 19.14, 19.12, 18.51, 19.43, 31.5) 

BfCr022021 <-c(64.24, 42.7, 56.5, 49.51,72.75 ,96.95 ,39.28 ,53.61 ,48.3 ,65.55 ,66.71)


ChCr012020 <-c(72.17,70.11,53.01,28.47,42.85,55.24,46.08,51.23,49.44,52.35,46.59,45.91)

ChCr012021 <-c(180.78,138.41,156.83,110.98,150.78,158.58,133.42,190.51,128.66)


CmCr2020 <-c(3.93,12.62,10.32,5.13,6.21,11.7,7.2,9.26,10.14)

CmCr2021 <-c(29.56,26.56,28.74,33.25,35.18,18.28,29.03,33.86,45.51,21.18)


CsCr2020 <-c(96.05,92.68,75.37,58.71,61.73,62.81,85.3,100.79,82.86,108.86,306.73,116.73)

CsCr2021 <-c(304.08,194.52,182.04,256.86,257.4,384.08,272.82)


FdCr2020 <-c(76.99,79.5,63.7,49.01,48.89,83.7,57.88,75,94.6,108.98,75.3,90.77)

FdCr2021 <-c(101.48,91.18,139.98,100.02,113.56,162.7,113.76,147.37,156.65,163.9)


LrCr2020 <-c(57.18,60.2,46.58,33.25,43.55,49.9,53.95,62.53,60.22,82.18,106.57,66.26)

LrCr2021 <-c(99.56,81.95,173.09,93.69,109.66,221.24,100.63,122.89,144.19,173.68,249.57,121.61)


NoFr012020 <-c(36.86,34.86,28.96,14.97,26.04,29.17,22.82,25.73,21.08)

NoFr012021 <-c(93.23,70.65,153.38,101.12,92.99,178.4,75.12,95.87,112.3,123.08,89.09)


NoFr022020 <-c(33.3,34.78,29.99,18.08,27.93,31.32,20.56,23.84,24.13)

NoFr022021 <-c(81.56,64.24,162.56,96.76,81.65,158.3,68.52,93.81,115.72,129.76,144.05)


NoFr032020 <-c(12.78,14.49,6.71,4.47,7.89,9.81,7.34,8.24,6.04)

NoFr032021 <-c(20.13,21.98,25.85,28.61,26.49,38.89,22.72,35.91,45.91,59.88,30.3)


NrCr2020 <-c(203.74,185.57,190.33,139.2,144.27,144.88,177.89,183.79,200.67,175.99,276.43,315.92)

NrCr2021 <-c(1408.33,420.83,372,558.89,582.3,556.8)


OhRv012020 <-c(26.26
,19.06
,42.7
,11.63
,11.26
,18.13
,29.31
,21.37
,27.58
,49.48
,22.83)

OhRv012021 <-c(60.56
,91.66
,142.49
,125.56)


OhRv022020 <-c(21.52
,18.97
,16.52
,19.87
,12.82
,17.28
,39.82
,35.35
,44.37
,59.68
,24.52
,27.12)

OhRv022021 <-c(52.56
,53.28
,50.14
,61.94
,58.43
,64.1
,68.04
,59.91
,86.29
,154.87
,141.38)


PrCr2020 <-c(37.38
,31.83
,30.39
,16.78
,18.99
,21.79
,18.18
,31.27
,34.16
,50.4
,30.17
,35.1)

PrCr2021 <-c(59.17
,53.88
,106.63
,60.16
,71.11
,119.22
,53.54
,65.34
,86.1
,110.5
,151.1
,69.41)


ShCr022020 <-c(59.29
,61.66
,110.44
,61.37
,52.19
,110.65
,43.02
,45.88
,40.03)

ShCr022021 <-c(222.45
,140.29
,381.81
,318.61
,123.26
,372.98
,139.24
,172.4
,161.85
,247.4
,159.29)


ShCr052020 <-c(15.39
,27.81
,14.35
,23.16
,26.17
,33.14
,20.48)

ShCr052021 <-c(66.92
,62.72
,103.94)


ShCr062020 <-c(33.56
,75.47
,111.56
,71.29
,65.45
,72.55
,36.73
,52.61
,35.98)

ShCr062021 <-c(400
,188.69
,440.05
,393.61
,184.62
,351.26
,190.35
,219.76
,187.69
,256.27
,147.48)


WdCr2020 <-c(75.44
,73.37
,59.65
,43.66
,51.82
,49.04
,52.15
,62.53
,65
,85.3
,238.62
,70.58)

WdCr2021 <-c(191.1
,122
,204.73
,233.36)


WeCr032020 <-c(38.61
,43.15
,46.87
,36.48
,9.63
,19.1
,30.12
,27.54
,29.01
,31.35
,27.42
,100.09
,38.78)

WeCr032021 <-c(82.55
,66.19
,126.95
,70.73
,87.62
,239.98
,45.74
,91.39
,112.62
,114.22
,149.46
,68.61)


WeCr072020 <-c(34.16
,39.25
,26
,15.55
,20.76
,27.09
,30.35
,29.81
,35.73
,48.51
,50.75)

WeCr072021 <-c(83.06
,71.78
,169.6
,98.22
,158.05
,248.22
,71.41
,100.62
,131.07
,147.33
,244.41)


WeCr092020 <-c(25.83
,26.61
,37.6
,23.18
,6.37
,9.69
,18.33
,13.14
,12.31
,19.67
,17.8
,16.96
,20.43)

WeCr092021 <-c(57.66
,58.32
,68.16
,48.78
,64.43
,72.52
,26.8
,47.36
,50.62
,72.43
,98
,41.46)


WrCr2020 <-c(4.23
,2.21
,2.53
,4.87
,6.49
,4.11
,4.59
,2.95)

WrCr2021 <-c(7.71
,8.26
,7.8
,7.41
,8.75
,7.76
,13.42
,15.01
,14.48
,15.13
,12.85)

```

###Chloride t-tests all are significant
```{r}
t.test(BfCr022020, BfCr022021, alternative = "two.sided", var.equal = TRUE)

t.test(ChCr012020, ChCr012021, alternative = "two.sided", var.equal = TRUE)

t.test(CmCr2020, CmCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(CsCr2020, CsCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(FdCr2020, FdCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(LrCr2020, LrCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr012020, NoFr012021, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr022020, NoFr022021, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr032020, NoFr032021, alternative = "two.sided", var.equal = TRUE)

t.test(NrCr2020, NrCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(OhRv012020, OhRv012021, alternative = "two.sided", var.equal = TRUE)

t.test(OhRv022020, OhRv022021, alternative = "two.sided", var.equal = TRUE)

t.test(PrCr2020, PrCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr022020, ShCr022021, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr052020, ShCr052021, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr062020, ShCr062021, alternative = "two.sided", var.equal = TRUE)

t.test(WdCr2020, WdCr2021, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr032020, WeCr032021, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr072020, WeCr072021, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr092020, WeCr092021, alternative = "two.sided", var.equal = TRUE)

t.test(WrCr2020, WrCr2021, alternative = "two.sided", var.equal = TRUE)

```

###Mann-Whitney U test 19 significant out of 21
```{r}
wilcox.test(BfCr022020, BfCr022021)

wilcox.test(ChCr012020, ChCr012021)

wilcox.test(CmCr2020, CmCr2021)

wilcox.test(CsCr2020, CsCr2021)

wilcox.test(FdCr2020, FdCr2021)

wilcox.test(LrCr2020, LrCr2021)

wilcox.test(NoFr012020, NoFr012021)

wilcox.test(NoFr022020, NoFr022021)

wilcox.test(NoFr032020, NoFr032021)

wilcox.test(NrCr2020, NrCr2021)

wilcox.test(OhRv012020, OhRv012021)

wilcox.test(OhRv022020, OhRv022021)

wilcox.test(PrCr2020, PrCr2021)

wilcox.test(ShCr022020, ShCr022021)

wilcox.test(ShCr052020, ShCr052021)

wilcox.test(ShCr062020, ShCr062021)

wilcox.test(WdCr2020, WdCr2021)

wilcox.test(WeCr032020, WeCr032021)

wilcox.test(WeCr072020, WeCr072021)

wilcox.test(WeCr092020, WeCr092021)

wilcox.test(WrCr2020, WrCr2021)
```



#Winter Conductivity 
```{r}
WCBfCr0220 <-c(315
,474.6
,528.8
,343.7
,405
,455.5
,423.1
,402.5
,395.6)

WCBfCr0221 <-c(569.1
,509.6
,488.5
,508.5
,532.5
,545.9
,405.7
,473.2
,497.1
,475.5
,484.6)


WCChCr0120 <-c(1285
,1379
,1116
,871
,853.1
,1177
,955
,888
,846
,693.4
,822
,941)

WCChCr0121 <-c(1712
,2330
,2996
,1200
,1518
,1718
,1701
,1669
,1043)


WCCmCr20 <-c(295.1
,473.7
,528.8
,349.1
,391.9
,441.2
,343.6
,412.1
,405.6)

WCCmCr21 <-c(546.9
,504
,487.8
,485.1
,493.5
,397
,465.7
,477.8
,456.6
,400.1)


WCCsCr20 <-c(937
,947
,841
,736.7
,750.7
,900
,808.1
,784.3
,741.2
,661.8
,1153
,829)

WCCsCr21 <-c(1224
,929
,972
,1154
,1075
,1098
,1074)


WCFdCr20 <-c(667.5
,685.5
,595.1
,591.7
,609.7
,688.9
,686.7
,628.6
,628.4
,568.8
,643.8
,636.8)

WCFdCr21 <-c(686.8
,621.8
,673.8
,678.8
,702.8
,651.4
,670.2
,702.1
,738
,665.1)


WCLrCr20 <-c(638
,662.1
,607.3
,588
,609.6
,677.5
,641.5
,619
,620.4
,562
,747.6
,614.2)

WCLrCr21 <-c(710
,617.4
,721
,656.6
,708.3
,739.5
,668.4
,688.2
,743.1
,711.2
,677.5
,713.2)

WCLrCr19 <-c(312,
317,
324,
333,
339,
344,
351,
361,
381,
390,
415,
423)


WCNoFr0120 <-c(644.5
,737.5
,628.8
,510
,539.1
,618.4
,593
,565.1
,379.2)

WCNoFr0121 <-c(1037
,748.7
,844
,805.3
,863.4
,803.5
,607.3
,700.9
,749.9
,729.2
,682.2)

WCNoFr0119 <-c(309,
347,
351,
411)


WCNoFr0220 <-c(338.1
,621.6
,327.9
,440.8
,461.6
,521.6
,504.8
,458.5
,489.9)

WCNoFr0221 <-c(656.8
,590.3
,741.9
,631.6
,655.4
,577.3
,523.7
,587.7
,612.7
,598.1
,692.8)

WCNoFr0219 <-c(309,
347,
351,
368,
411)


WCNoFr0320 <-c(439.1
,499.4
,419.7
,338.6
,359.7
,424.4
,386.1
,376
,417)

WCNoFr0321 <-c(513.6
,466.4
,469.2
,471.6
,508
,437.8
,391.1
,452.1
,455.6
,446.2
,368.5)

WCNoFr0319 <-c(309,
351,
368,
411)


WCNrCr20 <-c(1823
,1729
,2297
,1678
,1435
,1337
,1724
,1466
,1445
,1355
,1213
,1575)

WCNrCr21 <-c(3193
,2076
,2374
,2856
,2895
,1955)


WCOhRv0120 <-c(278
,245.5
,341.2
,326.9
,224.2
,252.9
,279.6
,250.4
,269
,292.1
,284.8)

WCOhRv0121 <-c(251.7
,360.4
,426.1
,587.9)

WCOhRv0119 <-c(311,
318,
324,
333,
339,
344,
351,
361,
390,
415)


WCOhRv0220 <-c(276.3
,244.2
,342.3
,331.1
,225.6
,243.9
,274.4
,196.1
,224.9
,294.1
,244.5
,271.5)

WCOhRv0221 <-c(374.5
,313.8
,299.1
,235.6
,280
,249.5
,244.5
,279.7
,343
,434.2
,544.3)

WCOhRv0219 <-c(311,
318,
324,
333,
339,
344,
351,
361,
390,
415)


WCPrCr20 <-c(553.9
,572.3
,527.8
,496.5
,484
,570.3
,556.6
,511
,508
,437.8
,518.3
,531.8)

WCPrCr21 <-c(613.8
,556.5
,638.2
,598.8
,620.2
,609.8
,552
,577.1
,633.8
,605.2
,606.5
,563.2)

WCPrCr19 <-c(312,
317,
324,
333,
339,
344,
351,
361,
381,
390,
415,
423)


WCShCr0220 <-c(754
,764.2
,1065
,703.7
,686.4
,995
,699.1
,662.1
,640.9)

WCShCr0221 <-c(1401
,947
,1512
,1499
,953
,1412
,746.6
,910.4
,994
,1245
,1025)

WCShCr0219 <-c(309,
347,
351,
368,
411)


WCShCr0520  <-c(515
,568.6
,408.4
,420.6
,493.6
,487.3
,450.2)

WCShCr0521 <-c(599.2
,482.8
,534.1)


WCShCr0620  <-c(734
,829
,1235
,747.8
,724.1
,832.6
,713.2
,718.1
,694.6)

WCShCr0621 <-c(1914
,1135
,1685
,1670
,1218
,1340
,1088
,1146
,1121
,1294
,979)


WCWdCr20 <-c(744
,737
,669.8
,652.9
,663.8
,680.9
,697.3
,666.9
,675.4
,614.3
,1002
,689.5)

WCWdCr21 <-c(800.8
,716.7
,819.8
,744.9)

WcWdCr19 <-c(311,
317,
324,
333,
339,
344,
351,
361,
381,
390,
415,
423)


WCWeCr0320 <-c(447.7
,477.9
,568.6
,453.3
,319.1
,280.3
,480.2
,427.4
,327.3
,365.1
,237
,578.3
,456.6)

WCWeCr0321 <-c(618.7
,540.5
,592.2
,549.1
,590.8
,615.7
,394.1
,521.2
,578.9
,602.1
,485.8
,439)

WCWeCr0319 <-c(312,
317,
324,
333,
339,
344,
351,
361,
381,
390,
415,
423)


WCWeCr0720 <-c(455.9
,485.8
,385.5
,359.4
,367.2
,481.5
,431.4
,380.5
,390.2
,323.1
,494.5)

WCWeCr0721 <-c(534.2
,546.9
,647.5
,627.7
,743.7
,732
,461.2
,548.5
,623.5
,587.1
,647.2)

WCWeCr0719 <-c(312,
317,
324,
333,
339,
344,
351,
361,
390,
415,
423)


WCWeCr0920 <-c(438.4
,448
,556
,397.8
,282.9
,252.7
,460.2
,429.6
,287
,352.5
,212.4
,386.4
,412.3)

WCWeCr0921 <-c(540.9,
505.4,
519.9,
488.6,
483.3,
487.6,
385.9,
457.9,
471.2,
432.3,
399,
386.5)


WCWrCr20 <-c(422.5,
420,
335.5,
346.8,
425.9,
396.7,
357.1,
415.9)

WCWrCr21 <-c(462.6,
419.6,
362.3,
417.7,
449.2,
350.3,
362.7,
421.1,
417,
396.4,
300.7)

```


### ANOVA for winter sites for 3 years
```{r}
wlrcraov <- read.csv("winter lrcr.csv")
wnofr01aov <- read.csv("winter nofr01.csv")
wnofr02aov <- read.csv("winter nofr02.csv")
wnofr03aov <- read.csv("winter nofr03.csv")
wohrv01aov <- read.csv("winter ohrv01.csv")
wohrv02aov <- read.csv("winter ohrv02.csv")
wshcr02aov <- read.csv("winter shcr02.csv")
wwdcraov <- read.csv("winter wdcr.csv")
wprcraov <- read.csv("winter prcr.csv")
wwecr03aov <- read.csv("winter wecr03.csv")
wwecr07aov <- read.csv("winter wecr07.csv")

winterLrCrsum <- aov(Conductivity ~ Site, data=wlrcraov)
summary(winterLrCrsum)
TukeyHSD(winterLrCrsum)

winterNoFr01sum <- aov(Conductivity ~ Site, data=wnofr01aov)
summary(winterNoFr01sum)
TukeyHSD(winterNoFr01sum)

winterNoFr02sum <- aov(Conductivity ~ Site, data=wnofr02aov)
summary(winterNoFr02sum)
TukeyHSD(winterNoFr02sum)

winterNoFr03sum <- aov(Conductivity ~ Site, data=wnofr03aov)
summary(winterNoFr03sum)
TukeyHSD(winterNoFr03sum)

winterOhRv01sum <- aov(Conductivity ~ Site, data=wohrv01aov)
summary(winterOhRv01sum)
TukeyHSD(winterOhRv01sum)

winterOhRv02sum <- aov(Conductivity ~ Site, data=wohrv02aov)
summary(winterOhRv02sum)
TukeyHSD(winterOhRv02sum)

winterShCr02sum <- aov(Conductivity ~ Site, data=wshcr02aov)
summary(winterShCr02sum)
TukeyHSD(winterShCr02sum)

winterWdCrsum <- aov(Conductivity ~ Site, data=wwdcraov)
summary(winterWdCrsum)
TukeyHSD(winterWdCrsum)

winterPrCrsum <- aov(Conductivity ~ Site, data=wprcraov)
summary(winterPrCrsum)
TukeyHSD(winterPrCrsum)

winterWeCr03sum <- aov(Conductivity ~ Site, data=wwecr03aov)
summary(winterWeCr03sum)
TukeyHSD(winterWeCr03sum)

winterWeCr07sum <- aov(Conductivity ~ Site, data=wwecr07aov)
summary(winterWeCr07sum)
TukeyHSD(winterWeCr07sum)

```
19 = Dec 2018 to Feb 2019, 20 = Dec 2019 to Feb 2020 and 21 = Dec 2019 to Feb 2021

### Dunn Tests
```{r}
library(FSA)

dunnTest(Conductivity ~ Site, data=wlrcraov)

dunnTest(Conductivity ~ Site, data=wnofr01aov)

dunnTest(Conductivity ~ Site, data=wnofr02aov)

dunnTest(Conductivity ~ Site, data=wnofr03aov)

dunnTest(Conductivity ~ Site, data=wohrv01aov)

dunnTest(Conductivity ~ Site, data=wohrv02aov)

dunnTest(Conductivity ~ Site, data=wshcr02aov)

dunnTest(Conductivity ~ Site, data=wprcraov)

dunnTest(Conductivity ~ Site, data=wwdcraov)

dunnTest(Conductivity ~ Site, data=wwecr03aov)

dunnTest(Conductivity ~ Site, data=wwecr07aov)
```

### Kruskal test
```{r}
kruskal.test(Conductivity ~ Site, data=wlrcraov)

kruskal.test(Conductivity ~ Site, data=wnofr01aov)

kruskal.test(Conductivity ~ Site, data=wnofr02aov)

kruskal.test(Conductivity ~ Site, data=wnofr03aov)

kruskal.test(Conductivity ~ Site, data=wohrv01aov)

kruskal.test(Conductivity ~ Site, data=wohrv02aov)

kruskal.test(Conductivity ~ Site, data=wshcr02aov)

kruskal.test(Conductivity ~ Site, data=wprcraov)

kruskal.test(Conductivity ~ Site, data=wwdcraov)

kruskal.test(Conductivity ~ Site, data=wwecr03aov)

kruskal.test(Conductivity ~ Site, data=wwecr07aov)
```

### Boxplot
```{r}
boxplot(Conductivity ~ Site, data=wlrcraov)

boxplot(Conductivity ~ Site, data=wnofr01aov)

boxplot(Conductivity ~ Site, data=wnofr02aov)

boxplot(Conductivity ~ Site, data=wnofr03aov)

boxplot(Conductivity ~ Site, data=wohrv01aov)

boxplot(Conductivity ~ Site, data=wohrv02aov)

boxplot(Conductivity ~ Site, data=wshcr02aov)

boxplot(Conductivity ~ Site, data=wprcraov)

boxplot(Conductivity ~ Site, data=wwdcraov)

boxplot(Conductivity ~ Site, data=wwecr03aov)

boxplot(Conductivity ~ Site, data=wwecr07aov)
```



###Conductivity t-tests 13 are significant out of 21
```{r}
t.test(WCBfCr0220, WCBfCr0221, alternative = "two.sided", var.equal = TRUE)

t.test(WCChCr0120, WCChCr0121, alternative = "two.sided", var.equal = TRUE)

t.test(WCCmCr20, WCCmCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCCsCr20, WCCsCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCFdCr20, WCFdCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCLrCr20, WCLrCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCNoFr0120, WCNoFr0121, alternative = "two.sided", var.equal = TRUE)

t.test(WCNoFr0220, WCNoFr0221, alternative = "two.sided", var.equal = TRUE)

t.test(WCNoFr0320, WCNoFr0321, alternative = "two.sided", var.equal = TRUE)

t.test(WCNrCr20, WCNrCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCOhRv0120, WCOhRv0121, alternative = "two.sided", var.equal = TRUE)

t.test(WCOhRv0220, WCOhRv0221, alternative = "two.sided", var.equal = TRUE)

t.test(WCPrCr20, WCPrCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCShCr0220, WCShCr0221, alternative = "two.sided", var.equal = TRUE)

t.test(WCShCr0520, WCShCr0521, alternative = "two.sided", var.equal = TRUE)

t.test(WCShCr0620, WCShCr0621, alternative = "two.sided", var.equal = TRUE)

t.test(WCWdCr20, WCWdCr21, alternative = "two.sided", var.equal = TRUE)

t.test(WCWeCr0320, WCWeCr0321, alternative = "two.sided", var.equal = TRUE)

t.test(WCWeCr0720, WCWeCr0721, alternative = "two.sided", var.equal = TRUE)

t.test(WCWeCr0920, WCWeCr0921, alternative = "two.sided", var.equal = TRUE)

t.test(WCWrCr20, WCWrCr21, alternative = "two.sided", var.equal = TRUE)
```

###Mann-Whitney U test 12 significant out of 21
```{r}
wilcox.test(WCBfCr0220, WCBfCr0221)

wilcox.test(WCChCr0120, WCChCr0121)

wilcox.test(WCCmCr20, WCCmCr21)

wilcox.test(WCCsCr20, WCCsCr21)

wilcox.test(WCFdCr20, WCFdCr21)

wilcox.test(WCLrCr20, WCLrCr21)

wilcox.test(WCNoFr0120, WCNoFr0121)

wilcox.test(WCNoFr0220, WCNoFr0221)

wilcox.test(WCNoFr0320, WCNoFr0321)

wilcox.test(WCNrCr20, WCNrCr21)

wilcox.test(WCOhRv0120, WCOhRv0121)

wilcox.test(WCOhRv0220, WCOhRv0221)

wilcox.test(WCPrCr20, WCPrCr21)

wilcox.test(WCShCr0220, WCShCr0221)

wilcox.test(WCShCr0520, WCShCr0521)

wilcox.test(WCShCr0620, WCShCr0621)

wilcox.test(WCWdCr20, WCWdCr21)

wilcox.test(WCWeCr0320, WCWeCr0321)

wilcox.test(WCWeCr0720, WCWeCr0721)

wilcox.test(WCWeCr0920, WCWeCr0921)

wilcox.test(WCWrCr20, WCWrCr21)
```



#Summer Chloride
```{r}
BfCr01cl19 <-c(18.21,
14.4,
20.4,
20.23,
18.41,
16.53,
14.58,
11.81,
20.98)

BfCr01cl20 <-c(20.47,
13.74,
9.45,
30.06,
35.93,
33.8,
33.38,
40.22,
24.29,
23.44,
30.39)


BfCr02cl19 <-c(19.72,
14.99,
19.93,
18.34,
18.8,
18.57,
15.74,
12.88,
25.1)

BfCr01cl20 <-c(12.54,
14.16,
32.51,
35.71,
47.86,
30.86,
61.55,
32.34,
42.46,
36.75)


ChCr01cl19 <-c(34.53,
60.8,
77.81,
70.49,
69.32,
73.97,
89.99,
144.52)

ChCr01cl20 <-c(70.74,
68.9,
83.42,
108.41,
133.43,
141.34,
156.99,
199.23,
95.77,
135.32,
139.95,
158.2,
120.38)


CmCrcl19 <-c(4.98,
16.78,
16.19,
13.1,
8.01)

CmCrcl20 <-c(30.84,
9.29,
25.06,
29.7,
25.37,
39.91,
19.04,
24.45,
36.72,
27.45)


CsCrcl19 <-c(98.55,
131.22,
139,
93.6,
106.31,
57.56,
88.5,
96.04)

CsCrcl20 <-c(60.61,
72.93,
75.7,
133.07,
160.94,
73.53,
174,
174.4,
115.63,
132.86,
123.06,
130.33)


FdCrcl19 <-c(55.49,
132.01,
108.81,
74.45,
58.4,
56.69,
94.78)

FdCrcl20 <-c(57.34,
53.16,
65.37,
74.5,
114.43,
147.67,
175.72,
155.96,
73.55,
85.47,
87.73,
125.8,
70.75)

LrCrcl19 <-c(47.77,
46.17,
53.99,
40.18,
31.19,
33.4,
34.86,
50.96,
62.98,
28.47,
43.83,
47.02,
46.22,
42.84,
40.71)

LrCrcl20 <-c(49.43,
38.59,
49.02,
65.21,
86.92,
54.56,
94.6,
108.77,
53.19,
63.46,
95.98,
86.76,
68.07)


NoFr01cl19 <-c(36.56,
35.26,
42.25,
34.21,
29.65,
26.84,
26.29,
24.64,
26.73,
32.6)

NoFr01cl20 <-c(48.22,
23.74,
27.74,
57.51,
70.79,
69.19,
70.98,
87.41,
45.38,
61.52,
63.95,
16.13,
60.67)


NoFr02cl19 <-c(45.1,
37.69,
42.83,
33.09,
45.05,
27.06,
30.89,
28.81)

NoFr02cl20 <-c(62.9,
29.4,
29.63,
63.19,
78.47,
89.91,
82.01,
93.31,
53.77,
64.46,
71.99,
81.31,
80.89)


NoFr03cl19 <-c(12.17,
15.22,
13.01,
8.97,
8.79,
4.56,
8.3,
5.38,
10.17)

NoFr03cl20 <-c(20.51,
7.85,
9.75,
15.41,
21.35,
15.16,
14.38,
21.34,
14.49,
15.61,
15.16,
70.25,
15.6)


NrCrcl19 <-c(216.63,
255.74,
228.85,
246.81,
194.02,
165.27,
201.12,
154.45)

NrCrcl20 <-c(276.53,
129.11,
110.28,
161.83,
195.25,
124.12,
218.38,
209.82,
200.2,
205.47)


OhRv01cl19 <-c(12,
7.97,
15.31,
14.25,
9.87,
23.83,
15.54,
28.44,
25.06,
21.08,
16.28,
15.89,
22.78,
25.28)

OhRv01cl20 <-c(45.18,
25.76,
25.41,
39.65,
49.13,
48.88,
48.94,
67.64,
57.45,
34.48)


OhRv02cl19 <-c(10.48,
5.34,
8.63,
7.23,
6.27,
25.69,
8.29,
25.25,
23.79,
14.14,
19.28,
22.92,
19.99,
27.13)

OhRv02cl20 <-c(41.08,
26.44,
26.77,
38.45,
49.76,
49.36,
49.59,
69.76,
60.45,
41.47,
42.97,
42.47,
35.88)


PrCrcl19 <-c(29.99,
30.96,
42.89,
31.05,
27.7,
33.62,
21.38,
25.22,
22.05,
23.75,
23.73)

PrCrcl20 <-c(43.3,
19.75,
21.7,
37.91,
46.1,
52.61,
57.67,
60.21,
34.55,
34.53,
42.25,
53.14,
43.88)


ShCr02cl19 <-c(235.39,
154.97,
143.47,
88.38,
48.25,
41.43,
83.27,
29.85,
156.3,
270.15)

ShCr02cl20 <-c(88.96,
151.46,
51.4,
421.41,
195.4,
108.75,
554.77,
356.83,
165.38,
228.04,
117.05,
113.13,
159.54)


ShCr03cl19<-c(42.63,
38.61,
40.64,
30.01,
39.9,
27.75,
28.6,
26.61)

ShCr03cl20 <-c(49.55,
30.84,
27.8,
48.99,
69.58,
69.92,
72.3)


ShCr05cl19 <-c(27.07,
28.45,
21.73,
20.7,
21.81)

ShCr05cl20 <-c(59.77,
22.7,
23.9,
40.4,
57.31,
64.96,
54.65,
65.74,
29.12,
36.98,
42.4,
51.28,
40.77)


ShCr06cl19 <-c(53.8,
162.79,
175.45,
213.89,
78.14,
267.44,
148.06)

ShCr06cl20 <-c(91.17,
157.92,
66.1,
312.81,
161.31,
215.3,
183.43,
585.27,
124.21,
155.34,
337.84,
244.26,
406.73)

WdCrcl19 <-c(62.89,
68.1,
70.7,
61.5,
41.56,
66.02,
40.14,
51.61,
62.39,
35.85,
51.89,
47.94,
51.24,
50.37,
57.55)

WdCrcl20 <-c(78.9,
53.13,
59.74,
97.08,
86.69)


WeCr03cl19 <-c(21.51,
27.39,
34.27,
34.69,
24.87,
38.17,
15.56,
24.89,
26.98,
15.79,
32.07,
35.19,
26.68,
31.75,
43.08)

WeCr03cl20 <-c(50.82,
19.46,
35.19,
57.63,
63.09,
76.65,
75.42,
89.26,
50.98,
45.78,
60.44,
72.59,
65.38)


WeCr07cl19 <-c(42.4,
40.13,
47.48,
46.95,
40.16,
43,
30.7,
34.3,
42.06,
23.35,
44.22,
55.2)

WeCr07cl20 <-c(58.14,
28.47,
35.96,
60.64,
78.31,
81.74,
88.57,
47.91,
62.3,
62.59,
80.85,
66.65)


WeCr09cl19 <-c(25.47,
25.75,
35.24,
34.4,
25.34,
30.17,
21.65,
23.71,
17.43,
23.72,
23.67)

WeCr09cl20 <-c(39.7,
13.85,
22.68,
39.54,
53.25,
63.55,
46.32,
69.97,
50.09,
31.1,
38.15,
47.46,
54.48)


WeCr11cl19 <-c(26.51,
66.72,
55.54,
33.26,
30.42,
37.01,
36.48,
51.97)

WeCr11cl20 <-c(62.46,
26.99,
34.8,
52.12,
65.01,
73.03,
72.41,
48.12,
58.33,
72.69,
62.33)


WrCrcl19 <-c(2,
5.44,
6.07,
3.61,
5.06,
2.3)

WrCrcl20 <-c(9.36,
2.82,
3.07,
8.89,
7.76,
11.6,
10.31,
5.44,
4.99,
7.94,
7.11,
5.63)

```

###t-tests summer chloride 16 significant out of 24
```{r}
t.test(BfCr01cl19, BfCr01cl20, alternative = "two.sided", var.equal = TRUE)

t.test(BfCr02cl19, BfCr01cl20, alternative = "two.sided", var.equal = TRUE)

t.test(CmCrcl19, CmCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(ChCr01cl19, ChCr01cl20, alternative = "two.sided", var.equal = TRUE)

t.test(CsCrcl19, CsCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr01cl19, NoFr01cl20, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr02cl19, NoFr02cl20, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr03cl19, NoFr03cl20, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr02cl19, ShCr02cl20, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr03cl19, ShCr03cl20, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr05cl19, ShCr05cl20, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr06cl19, ShCr06cl20, alternative = "two.sided", var.equal = TRUE)

t.test(WrCrcl19, WrCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(WdCrcl19, WdCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(FdCrcl19, FdCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(PrCrcl19, PrCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(LrCrcl19, LrCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(NrCrcl19, NrCrcl20, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr03cl19, WeCr03cl20, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr07cl19, WeCr07cl20, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr09cl19, WeCr09cl20, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr11cl19, WeCr11cl20, alternative = "two.sided", var.equal = TRUE)

t.test(OhRv01cl19, OhRv01cl20, alternative = "two.sided", var.equal = TRUE)

t.test(OhRv02cl19, OhRv02cl20, alternative = "two.sided", var.equal = TRUE)
```

###Wilcox 12 were wignificant
```{r}
wilcox.test(BfCr01cl19, BfCr01cl20)

wilcox.test(BfCr02cl19, BfCr01cl20)

wilcox.test(CmCrcl19, CmCrcl20)

wilcox.test(ChCr01cl19, ChCr01cl20)

wilcox.test(CsCrcl19, CsCrcl20)

wilcox.test(NoFr01cl19, NoFr01cl20)

wilcox.test(NoFr02cl19, NoFr02cl20)

wilcox.test(NoFr03cl19, NoFr03cl20)

wilcox.test(ShCr02cl19, ShCr02cl20)

wilcox.test(ShCr03cl19, ShCr03cl20)

wilcox.test(ShCr05cl19, ShCr05cl20)

wilcox.test(ShCr06cl19, ShCr06cl20)

wilcox.test(WrCrcl19, WrCrcl20)

wilcox.test(WdCrcl19, WdCrcl20)

wilcox.test(FdCrcl19, FdCrcl20)

wilcox.test(PrCrcl19, PrCrcl20)

wilcox.test(LrCrcl19, LrCrcl20)

wilcox.test(NrCrcl19, NrCrcl20)

wilcox.test(WeCr03cl19, WeCr03cl20)

wilcox.test(WeCr07cl19, WeCr07cl20)

wilcox.test(WeCr09cl19, WeCr09cl20)

wilcox.test(WeCr11cl19, WeCr11cl20)

wilcox.test(OhRv01cl19, OhRv01cl20)

wilcox.test(OhRv02cl19, OhRv02cl20)
```







#Summer Conductivity
```{r}

BfCr0119 <-c(427.7,414.7,381.3,371.8,380.7,359.1,423,398.3,416,430.5,394)

BfCr0120 <-c(424.1,438.3,429.2,426.6,303,379.6,443.7,482.8,474.8,466.7,394.9,410.3,449.4)

BfCr0118 <-c(365.5,
451.8,
412.4,
416.2,
431.3,
448.7)


BfCr0219 <-c(445.5,428.6,414,398.1,398,378,449.5,441.5,431.9,457.5,395)

BfCr0220 <-c(465.6,476.2,485.5,466.8,500,462.2,539,623,480.8,430.9,518.6,543.2,588)

BfCr0218 <-c(406.9,
499.6,
450.8,
453.4,
484.5,
493)


ChCr0119 <-c(631,788,988,894,1089,1324,1555,1757,2244,2457,1216)

ChCr0120 <-c(1126,1295,1502,1743,1471,1754,2534,3186,4460,5120,4916,1734,3231,4030,4436,3234)


CmCr19 <-c(291.5,416.3,414.7,296.4,423.9,429.9)

CmCr20 <-c(426.6,457.7,473.7,461,474.7,507.4,496.2,507.9,463.2,399.6,516.4,499.1)


CsCr19 <-c(665,835,875,892,896,884,1057,1138,1261,1211,833)

CsCr20 <-c(767,909,983,1037,996,1161,1242,1370,848,1783,1357,807,1078,1054,1325,1272)


FdCr19 <-c(481.8,680,635,565,567,678,712,735)

FdCr20 <-c(621,671,685,704,655,706,544,730,784,924,750,551,687,708,781,464.8)


LrCr19 <-c(632,563.8,601,522.7,556.9,552.8,545,562,577,552,667,623,616,657,587,704,664,481.6,751)

LrCr20 <-c(576,642,566,675,627,674,518.7,676,528.1,777,634,501.5,636,700,710,658)

LrCr18 <-c(326.3,
632,
655,
680,
634,
609,
704,
685,
703)


NoFr0119 <-c(648,634,545.4,542,572,496.9,622,644,629,643,697,680,814)

NoFr0120 <-c(585,648,684,681,640,648,609,775,823,826,835,567,747,855,484.5,828)

NoFr0118 <-c(534.4,
622,
626,
623,
717,
725)


NoFr0219 <-c(529.4,517.2,483.4,477.6,498.2,541.9,546.6,481.1,575,663)

NoFr0220 <-c(479.6,522.2,550.7,555.6,507.8,493.1,483.8,593,520.8,617,571,495.4,608,647,650,651)


NoFr0319 <-c(413.2,378.9,388.6,387.8,360.8,420.2,441,444.7,447.1,458.4,445.4,495.2)

NoFr0320 <-c(418.6,430.8,445.9,441.8,401.5,384.4,384.2,454,474.2,469.5,463.8,409.6,461.8,476.2,847,465.7)

NoFr0318 <-c(397.7,
461.9,
439.9,
439.2,
451.4,
445.8)


NrCr19 <-c(2049,2112,2478,2263,2521,2247,2932,3096,3835,3750,2485)

NrCr20 <-c(2742,3345,3638,3951,2878,3710,3392,4140,922,4434,3025,3637,3823)


OhRv0119 <-c(231.6,221.1,220.4,190.2,215.2,228.3,245.5,254.1,256.4,296.9,266.4,273.5,308.1,313.6,384,398.6,409.9,368.8)

OhRv0120 <-c(341.4,325,371,405.7,434.8,330,402.2,407.2,443,411.3,399.2,388.6)

OhRv0118 <-c(360.9,
338,
341.7,
332.2,
371.3,
124,
378.6,
361.6)


OhRv0219 <-c(233.4,219.1,221.4,194,214.1,245.2,241.6,251.5,296.5,281.4,275.1,283.8,308.3,337.3,396,389.9,403.8,404.4,371.6)

OhRv0220 <-c(341,324.4,346,367.7,355,433.7,326.8,402.1,416.2,443.2,409.4,374.8,400.9,407.9,370.7,389.8)


PrCr19 <-c(546.8,513.3,513.2,477,483.5,477.9,467.2,454,479.3,525,561,580,448.8)

PrCr20 <-c(506.9,556,577.2,558,548.7,574,464.6,567,559,575,579,466.3,604,640,658,615)


ShCr0219 <-c(1445,1134,894,730,653,685,921,687,1200,1543,1162,1438,2180)

ShCr0220 <-c(834,717,842,1291,1472,880,2464,1451,1020,3369,1933,1047,1553,1219,1143,1366)

ShCr0218 <-c(759,
1223,
1144,
1084,
1181,
1205)


ShCr0319 <-c(624.5,607,534.6,521.9,563,604,612,509.2,674,804)

ShCr0320 <-c(557.5,615,657,662,584,643,592,742,817,840)


ShCr0519 <-c(448.8,451.9,499.1,513.6,450,538,630)

ShCr0520 <-c(480.1,507,537.6,493,542,457.6,569,645,645,592,406.4,573,599,627.5,581.1)


ShCr0619 <-c(583,942,1119,1219,932,1628,1140,1448,1727)

ShCr0620 <-c(820,846,1083,1527,1508,1014,1845,1205,1508,1492,2749,886,1267,2204,1584,2399)


WdCr19 <-c(700,669,703,614,612,614,595,618,592,654,710,664,656,710,708,760,745,639)

WdCr20 <-c(680,741,786,808,725,778,650,635)

WdCr18 <-c(725,
733,
772,
725,
770,
863,
822)


WeCr0319 <-c(446.1,462.5,434,396.8,418.1,440.2,327.8,373.3,393.1,449.5,483.7,491.3,499.7,538,544,557,566,438.5,529)

WeCr0320 <-c(458.7,524,464.5,552,439.1,545,487.5,558,615,637,545,480.2,530,582,640,646)

WeCr0318 <-c(504,
408,
489,
492,
478.3,
509,
527,
478.6,
517)


WeCr0719 <-c(493.6,468.3,461.7,441.6,477.6,465.5,378.1,427,478.1,396.2,525.7,573,619,434.2,594)

WeCr0720 <-c(434.2,508.8,454.4,561,496.7,587,552,571,560,598,474.8,607,656,705,665)

WeCr0718 <-c(475,
518,
533,
496,
544,
568,
547,
600)


WeCr0919 <-c(383.9,432.3,389.7,373.1,401.1,380,314.7,406,380.4,431,431.2,476.4,250.7)

WeCr0920 <-c(417.5,462.9,496.2,509,397.1,500,429.7,558,505,358.1,519,510,326,498.8,529.4,540.2)


WeCr1119 <-c(304.3,485.1,479.4,388.1,357.6,484.2,509.4,563,622,443.7)

WeCr1120 <-c(436,510,539,557,507.5,587,509.7,553,648,701,477.5,641,696,655)


WrCr19 <-c(277.6,384,397.1,326.4,447.5,407.3,447.1,486.8)

WrCr20 <-c(414.4,433.1,444.7,438.4,433.7,420.7,470.1,484.8,476.7,475.7,390.7,453.1,481.2,465.5,445.3)


```

### ANOVA for all three years of the sites that were sampled in all years
```{r}
condaov <- read.csv("Cond aov.csv")

allsites <- aov(Conductivity ~ Site, data=condaov)
summary(allsites)
TukeyHSD(allsites)
hist(condaov$Conductivity)

bfcr01aov <- read.csv("bfcr01 aov.csv")
bfcr02aov <- read.csv("bfcr02 aov.csv")
lrcraov <- read.csv("lrcr aov.csv")
nofr01aov <- read.csv("nofr01 aov.csv")
nofr03aov <- read.csv("nofr03 aov.csv")
ohrv01aov <- read.csv("ohrv01 aov.csv")
shcr02aov <- read.csv("shcr02 aov.csv")
wdcraov <- read.csv("wdcr aov.csv")
wecr03aov <- read.csv("wecr03 aov.csv")
wecr07aov <- read.csv("wecr07 aov.csv")

BfCr01sum <- aov(Conductivity ~ Site, data=bfcr01aov)
summary(BfCr01sum)
TukeyHSD(BfCr01sum)

BfCr02sum <- aov(Conductivity ~ Site, data=bfcr02aov)
summary(BfCr02sum)
TukeyHSD(BfCr02sum)

LrCrsum <- aov(Conductivity ~ Site, data=lrcraov)
summary(LrCrsum)
TukeyHSD(LrCrsum)

NoFr01sum <- aov(Conductivity ~ Site, data=nofr01aov)
summary(NoFr01sum)
TukeyHSD(NoFr01sum)

NoFr03sum <- aov(Conductivity ~ Site, data=nofr03aov)
summary(NoFr03sum)
TukeyHSD(NoFr03sum)

OhRv01sum <- aov(Conductivity ~ Site, data=ohrv01aov)
summary(OhRv01sum)
TukeyHSD(OhRv01sum)

ShCr02sum <- aov(Conductivity ~ Site, data=shcr02aov)
summary(ShCr02sum)
TukeyHSD(ShCr02sum)

WdCrsum <- aov(Conductivity ~ Site, data=wdcraov)
summary(WdCrsum)
TukeyHSD(WdCrsum)

WeCr03sum <- aov(Conductivity ~ Site, data=wecr03aov)
summary(WeCr03sum)
TukeyHSD(WeCr03sum)

WeCr07sum <- aov(Conductivity ~ Site, data=wecr07aov)
summary(WeCr07sum)
TukeyHSD(WeCr07sum)
```

### Dunn Tests
```{r}
library(FSA)

dunnTest(Conductivity ~ Site, data=bfcr01aov)

dunnTest(Conductivity ~ Site, data=bfcr02aov)

dunnTest(Conductivity ~ Site, data=lrcraov)

dunnTest(Conductivity ~ Site, data=nofr01aov)

dunnTest(Conductivity ~ Site, data=nofr03aov)

dunnTest(Conductivity ~ Site, data=ohrv01aov)

dunnTest(Conductivity ~ Site, data=shcr02aov)

dunnTest(Conductivity ~ Site, data=wdcraov)

dunnTest(Conductivity ~ Site, data=wecr03aov)

dunnTest(Conductivity ~ Site, data=wecr07aov)
```

### Kruskal test
```{r}
kruskal.test(Conductivity ~ Site, data=bfcr01aov)

kruskal.test(Conductivity ~ Site, data=bfcr02aov)

kruskal.test(Conductivity ~ Site, data=lrcraov)

kruskal.test(Conductivity ~ Site, data=nofr01aov)

kruskal.test(Conductivity ~ Site, data=nofr03aov)

kruskal.test(Conductivity ~ Site, data=ohrv01aov)

kruskal.test(Conductivity ~ Site, data=shcr02aov)

kruskal.test(Conductivity ~ Site, data=wdcraov)

kruskal.test(Conductivity ~ Site, data=wecr03aov)

kruskal.test(Conductivity ~ Site, data=wecr07aov)
```

### Box plot
```{r}
boxplot(Conductivity ~ Site, data=bfcr01aov)

boxplot(Conductivity ~ Site, data=bfcr02aov)

boxplot(Conductivity ~ Site, data=lrcraov)

boxplot(Conductivity ~ Site, data=nofr01aov)

boxplot(Conductivity ~ Site, data=nofr03aov)

boxplot(Conductivity ~ Site, data=ohrv01aov)

boxplot(Conductivity ~ Site, data=shcr02aov)

boxplot(Conductivity ~ Site, data=wdcraov)

boxplot(Conductivity ~ Site, data=wecr03aov)

boxplot(Conductivity ~ Site, data=wecr07aov)
```





###t-tests between 2019 and 2020 14 were significant
```{r}
t.test(BfCr0119, BfCr0120, alternative = "two.sided", var.equal = TRUE)

t.test(BfCr0219, BfCr0220, alternative = "two.sided", var.equal = TRUE)

t.test(CmCr19, CmCr20, alternative = "two.sided", var.equal = TRUE)

t.test(ChCr0119, ChCr0120, alternative = "two.sided", var.equal = TRUE)

t.test(CsCr19, CsCr20, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr0119, NoFr0120, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr0219, NoFr0220, alternative = "two.sided", var.equal = TRUE)

t.test(NoFr0319, NoFr0320, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr0219, ShCr0220, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr0319, ShCr0320, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr0519, ShCr0520, alternative = "two.sided", var.equal = TRUE)

t.test(ShCr0619, ShCr0620, alternative = "two.sided", var.equal = TRUE)

t.test(WrCr19, WrCr20, alternative = "two.sided", var.equal = TRUE)

t.test(WdCr19, WdCr20, alternative = "two.sided", var.equal = TRUE)

t.test(FdCr19, FdCr20, alternative = "two.sided", var.equal = TRUE)

t.test(PrCr19, PrCr20, alternative = "two.sided", var.equal = TRUE)

t.test(LrCr19, LrCr20, alternative = "two.sided", var.equal = TRUE)

t.test(NrCr19, NrCr20, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr0319, WeCr0320, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr0719, WeCr0720, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr0919, WeCr0920, alternative = "two.sided", var.equal = TRUE)

t.test(WeCr1119, WeCr1120, alternative = "two.sided", var.equal = TRUE)

t.test(OhRv0119, OhRv0120, alternative = "two.sided", var.equal = TRUE)

t.test(OhRv0219, OhRv0220, alternative = "two.sided", var.equal = TRUE)
```


###Mann-Whitney U 14 significant 2019 & 2020
```{r}
wilcox.test(BfCr0119, BfCr0120)

wilcox.test(BfCr0219, BfCr0220)

wilcox.test(CmCr19, CmCr20)

wilcox.test(ChCr0119, ChCr0120)

wilcox.test(CsCr19, CsCr20)

wilcox.test(NoFr0119, NoFr0120)

wilcox.test(NoFr0219, NoFr0220)

wilcox.test(NoFr0319, NoFr0320)

wilcox.test(ShCr0219, ShCr0220)

wilcox.test(ShCr0319, ShCr0320)

wilcox.test(ShCr0519, ShCr0520)

wilcox.test(ShCr0619, ShCr0620)

wilcox.test(WrCr19, WrCr20)

wilcox.test(WdCr19, WdCr20)

wilcox.test(FdCr19, FdCr20)

wilcox.test(PrCr19, PrCr20)

wilcox.test(LrCr19, LrCr20)

wilcox.test(NrCr19, NrCr20)

wilcox.test(WeCr0319, WeCr0320)

wilcox.test(WeCr0719, WeCr0720)

wilcox.test(WeCr0919, WeCr0920)

wilcox.test(WeCr1119, WeCr1120)

wilcox.test(OhRv0119, OhRv0120)

wilcox.test(OhRv0219, OhRv0220)
```










